Consistency scores in text data

### 2020-07-23 outputs/documents/paper.Rmd
write-up updates on transformer model and add more referenced literatures

The above examples using GPT-2 were task-agnostic but they were in need of fine-tuning.
These parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. GPT-3 can learn NLP tasks with few examples and without any task-specific dataset **(Keli add citation)**.

GPT-3 is pre-trained, and takes a sample of text as an input **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. 
**(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**

Deep language representations, e.g. those
learned by the Transformer (Vaswani et al., 2017)
via language modeling (Radford et al., 2018),
have been shown to implicitly capture useful semantic and syntactic properties of text solely by
arXiv:1906.08646v1 [cs.CL] 19 Jun 2019
unsupervised pre-training (Peters et al., 2018)

>>>>

GPT is a Transformer-based model that has over 175 billions of parameters. **(Keli add citation)**. Proposed by Vaswani et al., the Transformer is a novel network architecture that outperforms RNN-based models in computational efficiency **(Keli add citation)**. The parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. In recent years, the growth of parameters of transformer language models expands rapidly which accelerate the improvements in text synthesis and downstream NLP tasks **(Keli add citation)**.

GPT-3 can learn NLP tasks with few examples and without any task-specific dataset **(Keli add citation)**. OpenAI refers this ability as few-shot learning. GPT-3 is pre-trained, and takes a sample of text as an input **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. 
**(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**
